\section{Discussion}
\label{sec:discussion}

\subsection{Leaf flexibility reduces drag relative to a rigid physical model}
Drag/area ratio is 19\% higher in the rigid physical model compared to the live \Cxparadisi\ specimen (\fref{fig:results:dragarea}; \fref{tab:results:drag}). While the small number of replicates and measurement noise limit the strength of my conclusions, the results suggest leaf flexibility is able to reduce drag experienced by the whole plant. 

Slow motion video frames (\fref{fig:results:leafmovement}) suggest a mechanism: bending at the leaf petiole. As \fref{fig:results:leafmovement} shows, the leaves were able to bend quite far at their joints before further deforming to reduce drag. They also avoided rapid flapping through the rigidity offered by the petioles. It would appear that the petioles gave the leaves a pivot point which allowed them to reposition effectively, but the petioles' firm, single degree-of-freedom connections to the stem kept the leaves from experiencing vortex-induced rotational modes or the complex fluttering observed by \citet{miller2012reconfiguration}. 

\subsection{Vortex shedding off single leaves?}
The flapping about a single petiole axis (\fref{fig:results:leafmovement}) is potentially an example of vortex shedding. As the wind reaches the leaves, they block its motion and cause high pressure zones to build up on the windward side and low pressure zones to form on the leeward side. The differing pressures pull the leaf backward. The wind continues to push the pressure zones along the leaf, and when they finally meet they detach from the leaf and chase each other in circles (vortices). At this point they also stop creating pressure drag on the leaf, allowing it to return to its original position so that the process may start again. This behavior is common in structures when placed in fluid flow and can especially be seen in airplane wings as they fly through clouds or in swirling water long after a canoe paddle has made its mark; but here it might appear to be tuned so as to (1) not flutter the leaf to death and (2) destructively (incoherently) add the forces from individual leaves so as not to provide a single large, locked-in time-varying force on the whole plant. Such a phenomenon would depend on the flow velocity, leaf dimensions, and leaf stiffness (e.g. Strouhal number and nondimensional stiffness), and could be addressed further using smoke, dye visualization, or computational fluid dynamics (CFD). 

\subsection{Stem Flexibility}
While these results do show that a smaller load was made on the stem, there are considerable variables to be tested in the future. Because the drag force was measured on the trunk of the \Cxparadisi, the results are impacted by the degree to which the plant trunk counteracted the drag force. The spring constant of the plant's trunk was unknown, and the plant did deflect during the course of the test. In future experiments, the flexibility of the plant should either be accounted for or eliminated. To address the first option, the trunk's angular spring constant could be found experimentally before the experiment begins. To address the second option, the plant could be mounted on a rotating board so that the trunk would be unable to exert its equal and opposite reaction on the ground. Given the presence of the COVID-19 pandemic, neither of these options were reasonably attainable, but should be implemented in future tests.

\subsection{Where is flexibility most useful?}
My observations suggest that distal bending at the petioles and nearest the leaves allows for protective load shedding of wind loads in \Cxparadisi. The drag measurements were taken from a point halfway down the trunk of the plant and the model, and therefore did not capture the torque experienced by the petiole joints. Judging from the immense range of motion in all three axes shown in the slow motion videos, it is reasonable to assume that the leaves' movements produced disproportionately large torque on their petiole joints, while producing less drag on the entire plant when compared to a rigid model. 

The petiole joints are more likely to give under stress, before the plant itself is uprooted or a branch detached. Anecdotally, as the plant's caretaker, I have observed that high winds in the spring resulted in loss of several large leaves on this specimen. In each case the petiole was consistently the fracture point. The joints thus play a dual function, reducing the plant's overall drag while also reducing the negative effects of fluttering to the leaves themselves rather than the plant as a whole. In the highest winds, the petioles provide a sacrificial mechanism to reduce load and avoid catastrophic loss of the entire plant. 

This plant architecture presents possible solutions to engineering problems involving wind in similar human structures. For example, solar power is often implemented in the tropical areas where \Cxparadisi is native, but hurricanes hold the potential to destroy fields of fixed solar panels by pulling them from their support structures and throwing them, causing damage to the electrical infrastructure as well as shattered panels. Both of these outcomes would be less likely if solar panels were modeled after \Cxparadisi leaves by either making the panels themselves flexible or by installing a joined system which would allow them to pivot in the wind. Similar endeavors could be made to reduce the drag effects on other structures, such as signs and billboards.

% does this suggest anything useful for how engineered structures (solar cell arrays, etc) migth be designed for wind loads. 
