\documentclass[10pt]{article}

% Question: does spring constant of the stem or pencil matter?
% What is alt hypothesis what do we disprove?
% Are findings of any use for design of engineered devices? 

\title{Drag on leaves in wind and flow-induced shape reconfiguration in grapefruit, {\emph{Citrus $\times$ paradisi}} (Rutaceae)}
\author{Cameron Smith\thanks{Author is with the Department of Weapons, Robotics, and Control Engineering at the United States Naval Academy. Address for correspondence: \emph{m226072@usna.edu}}}
\date{\today}


\usepackage[separate-uncertainty=true]{siunitx}
\DeclareSIUnit{\year}{y}
\DeclareSIUnit{\inch}{in}
\DeclareSIUnit{\foot}{ft}
\DeclareSIUnit{\poundforce}{lbf}
\DeclareSIUnit{\pound}{lbm}
\DeclareSIUnit{\frame}{frame}
\usepackage{graphicx}
\usepackage[round,authoryear]{natbib}
\bibliographystyle{apalike}
\usepackage[plain]{fancyref}
\usepackage{listings}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{booktabs}
\lstset{%
  basicstyle=\ttfamily,
  columns=fullflexible,
  showstringspaces=false}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{%
  colorlinks=true,
  linkcolor=violet,
  urlcolor=blue,
  citecolor=blue}
\usepackage{svg}
%\usepackage{svg-extract}
\usepackage{fullpage}

\newcommand{\Citrusxparadisi}{\emph{Citrus $\times$ paradisi}}
\newcommand{\Cxparadisi}{\emph{C.~$\times$~paradisi}}
\newcommand{\Matlab}{Matlab}
\begin{document}

\maketitle
\begin{abstract}
This study was conducted to investigate how effectively citrus plants can change their structure to reduce drag in wind. Due to the COVID-19 outbreak, this study made use of an improvised flexure-based force sensor for drag. An elastic cord was attached to a young grapefruit (\Citrusxparadisi) plant and a rigid aluminum physical model of one of its leaves, in the presence of flow from a small fan.  Cord displacement was used to quantify drag, while the area normal to flow was obtained from image analysis using color thresholding and blob detection. The drag experienced by the rigid model was 19\% higher than the drag measured on the live plant. Slow motion video analysis indicated that this was the result of the citrus's ability to bend at the petiole. The extreme bending in several directions suggests a method of protective load shedding and may also indicate a potential way to avoid flow induced vibrational loads from vortex shedding.
\end{abstract}
{\scriptsize\textbf{Keywords: }grapefruit, \Citrusxparadisi, drag, leaf, petiole}

\input{intro.tex} %\section{Introduction}
\input{methods.tex} %\section{Methods and materials}
\input{results.tex} %\section{Results}
\input{discussion.tex} %\section{Discussion}

\section{Acknowledgements}
I thank John Trombetta, Alexis Pak, and Sofia Figueroa for their assistance as classmates in EW282D / EW496. USNA Biomechanics is supported by Lockheed Martin. 

% References
\bibliography{smith.bib}

\clearpage
\appendix
\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\thefigure}{S\arabic{figure}}
\input{method-details.tex}
\end{document}
